% --------------------------------
% Resume in Latex
% Author Chun-Ho (Hugo) Lin (1chooo) <hugo970217@gmail.com>
% License : MIT
% --------------------------------

% ---- Required Packages and Functions ----

\documentclass[a4paper, 11pt]{article}
\usepackage{latexsym}
\usepackage[dvipsnames]{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}    % Hide the link box
% \usepackage{hyperref}             % Show the link box
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage{helvet}                 % PSNFSS Font, in every TeX distribution
\renewcommand{\familydefault}{\sfdefault}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{}                          % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{
    left=1.4cm, 
    top=0.8cm, 
    right=1.2cm, 
    bottom=1cm
}

% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\usepackage{enumitem}
\setlist[itemize]{
    label=-, 
    leftmargin=0cm, 
    itemsep=0cm, 
    topsep=0cm
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{olive}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item[]
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{
    \begin{itemize}[leftmargin=*,labelsep=0mm]
}
\newcommand{\resumeHeadingSkillStart}{
    \begin{itemize}[
        leftmargin=*,
        itemsep=1.7mm, 
        rightmargin=2ex
    ]
}

\newcommand{\resumeItemListStart}{
    \begin{justify}\begin{itemize}[
        leftmargin=3ex, 
        rightmargin=2ex, 
        noitemsep,
        labelsep=1.2mm,
        itemsep=0.5mm
    ]\small
}

\newcommand{\resumeSubHeadingListEnd}{
    \end{itemize}
    \vspace{2mm}
}
\newcommand{\resumeHeadingSkillEnd}{
    \end{itemize}
    \vspace{-2mm}
}
\newcommand{\resumeItemListEnd}{
    \end{itemize}\end{justify}\vspace{-2mm}
}
\newcommand{\cvsection}[1]{
    \vspace{2mm}
    \begin{tcolorbox}
        \textbf{\large #1}
    \end{tcolorbox}
        \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
%---- End of Packages and Functions --------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Chun-Ho Lin} % Your Name
\newcommand{\course}{Dept. of Atmospheric Science, NCU.} % Your Program
\newcommand{\roll}{xxxxxxx} % Your Roll No.
\newcommand{\phone}{909 001 068} % Your Phone Number
\newcommand{\emaila}{hugo970217@gmail.com} %Email 1
\newcommand{\emailb}{lcho0127@g.ncu.edu.tw} %Email 2
\newcommand{\myScore}{}
\newcommand{\announcement}{B.S. in ATM, Minor in CS, NCU | Ex AWS, PEGATRON, eCloudValley}
% \newcommand{\myScore}{GPA: 3.11/4.30; Rank: 26/35}

\definecolor{linkcolour}{rgb}{0, 0.2, 0.6}
\hypersetup{
    colorlinks,
    breaklinks,
    urlcolor=linkcolour,
    linkcolor=linkcolour
}

\begin{document}
\fontfamily{cmr}\selectfont

% Set the footskip to the minimum required value
\setlength{\footskip}{4.08003pt}

%----------HEADING-----------------
\begin{center}
    \textbf{\huge \name}
\end{center}

\begin{center}
    \announcement
\end{center}

\begin{center}
    \href{tel:+886-\phone}{
        \underline{
            \raisebox{0.0\height}{\footnotesize \faPhone}\
            {(+886) \phone}
        }
    } |
    \href{mailto:\emaila}{
        \underline{
            \raisebox{0.0\height}{\footnotesize \faEnvelope}\
            {\emaila}
        }
    } |
    \href{https://www.1chooo.com/}{
        \underline{
            \raisebox{0.0\height}{\footnotesize \faGlobe}\
            {1chooo.com}
        }
    } |
    \href{https://github.com/1chooo}{
        \underline{
            \raisebox{0.0\height}{\footnotesize \faGithub}\
            {1chooo}
        }
    } |
    \href{https://www.linkedin.com/in/1chooo/}{
        \underline{
            \raisebox{0.0\height}{\footnotesize \faLinkedin}\
            {in/1chooo/}
        }
    }
\end{center}
  
\vspace{-4.0mm}

%-----------EDUCATION-----------------
% \input{education.tex}

\section{\textcolor{olive}{\textbf{Education}}}
	\resumeSubHeadingListStart
		
    \resumeSubheading
        {National Central University}
        {Sep. 2020 - Jun. 2024}
        {Bachelor of Science in Atmospheric Science, Minor Specialty in Computer Science \myScore}
        {\textcolor{gray}{\footnotesize{\faMapMarker}} Taoyuan, Taiwan}
		
        \vspace{-1.0mm}
            
        \resumeItemListStart
            \item {
                \textbf{Graduate-level Courses:}
                The Attack and Defense of Computers,
                Object-Oriented Analysis and Design
            }
            \item {
                \textbf{B.S.-level Courses:}
                Software Engineering,
                Principles of Programming Languages,
                Assembly Language and System Programming,
                Operating System,
                Computer Network,
                Algorithmics, 
                Data Structures, 
                Digital Design
            }
            \item {
                \textbf{TA:} 
                Linux and Edge Computing,
                Programming Python, 
                Weather and Artificial Intelligence
            }
        \resumeItemListEnd
		  
	\resumeSubHeadingListEnd

\vspace{-5.5mm}

%-----------Technical skills-----------------
\section{\textcolor{olive}{\textbf{Technical Skills}}}

    \vspace{1.0mm}

    \begin{itemize}[
        leftmargin=0.20in, 
        label={-}, 
        itemsep=-2pt, 
        topsep=0pt,
        rightmargin=0.10in
    ]
        \item Programmings: Python (primary), C++/C, Java, Go, TypeScript, JavaScript, X86 Assembly, \LaTeX
        \item DevOps: AWS, Docker, Git, Bash, GitHub Actions, Azure, Terraform, Kubernetes, mySQL, Redis
        \item ML/DL: LangChain, TensorFlow, Scikit-learn, Keras, Numpy, Pandas
    \end{itemize}

\vspace{-3.0mm}

%-----------PROFESSIONAL EXPERIENCE-----------------
\section{\textcolor{olive}{\textbf{Professional Experience}}}
    \resumeSubHeadingListStart
    
    \resumeSubheading
        {eCloudValley Digital Technology}
        {Mar. 2024 - May. 2024}
        {Cloud Engineer Intern}
        {\textcolor{gray}{\footnotesize{\faMapMarker}} New Taipei, Taiwan}

        \vspace{-1.0mm}

        \resumeItemListStart
            \item {Led a team of 5 to enhance issue pools with AWS Bedrock, boosting cloud support efficiency by 80\% through multi-language support and 95\% accurate image recognition. Honored as the top-achieving internship team.}
            \item {Utilized a serverless architecture on AWS Lambda, performing troubleshooting with CloudWatch, deployed via AWS CDK, and integrated with DynamoDB and Bedrock services.}
            \item {Documented issues in 10+ mock cases, such as VPC entry failures, EC2 Apache server restarts, and S3 photo access problems, and provided detailed solutions for interns. Refer \href{https://github.com/1chooo/ecv-training-materials/tree/main/msp/aws_challenge}{\underline{here}} for a comprehensive list.}
        \resumeItemListEnd

    \vspace{-1.0mm}
    
    \resumeSubheading
        {Amazon Web Services}
        {Aug. 2023 - Feb. 2024}
        {Cloud Ambassador Technical Support}
        {\textcolor{gray}{\footnotesize{\faMapMarker}} Taipei, Taiwan}

        \vspace{-1.0mm}

        \resumeItemListStart
            \item Educated 700+ cloud developers and achieved 96\% user satisfaction by conducting 2 technical workshops, developing an open-source project, and 1 UAD with AWS cloud services. Refer \href{https://github.com/aws-educate-tw/aws-line-business-card-workshop}{\underline{here}} for the source code.
            \item {Conducted a comprehensive 35+ page market research study on cloud suppliers as part of an 11-member team.}
        \resumeItemListEnd

    \vspace{-1.0mm}
    
    \resumeSubheading
        {PEGATRON Corporation}
        {Jul. 2023 - Aug. 2023}
        {Software Engineer Intern}
        {\textcolor{gray}{\footnotesize{\faMapMarker}} Taipei, Taiwan}
            
        \vspace{-1.0mm}
        
        \resumeItemListStart
            \item {Executed a POC, adapting an LLM model for Smart Manufacturing, and was awarded Silver internship team.}
            \item {Collaborated with a team of 5, utilized Git, a CI/CD pipeline, and followed an agile Scrum workflow.}
            \item {Implemented {Prompt Engineering} and {LangChain} for the {NVIDIA Ominerve visual robot}, enabling seamless speech/text operation, boosting test support by {83\%} across {6-11} scenarios with {85\%} stability.}
        \resumeItemListEnd

    \vspace{-1.0mm}
    
    \resumeSubheading
        {National Central University}
        {Jul. 2022 - Jan. 2023}
        {Website Developer}
        {\textcolor{gray}{\footnotesize{\faMapMarker}} Taoyuan, Taiwan}
            
        \vspace{-1.0mm}
        
        \resumeItemListStart
            \item Partnered with a team of 2 to develop a multi-user score management system for the Center for Teacher Education, reducing credit exemption processing time by 80\% and remotely maintaining the server via SSH.
        \resumeItemListEnd

    \vspace{-0.0mm}

    \resumeSubHeadingListEnd
  
\vspace{-5.5mm}

%-----------PROJECTS-----------------
\section{\textcolor{olive}{\textbf{Selected Projects}}}
    \resumeSubHeadingListStart

    \resumeSubheading
        {Refinaid: Bridging the Gap with AI For Everyone} % Project Name
        {Aug. 2023 - present*} % Event Dates
        {Founder | Fullstack Developer} % Role
        {\href{https://github.com/1chooo/refinaid}{\underline{\faGithub\ Code}} | \href{https://1chooo.github.io/refinaid}{\underline{{\faBook}\ Docs}}} % Project Resources

        \vspace{-1.0mm}

        \resumeItemListStart
            \item {Built 2 low-code platforms, SIMPLE-AI and Chatger, while serving as a TA for 3 courses, offering a {no-code interface} for training AI/ML/DL models and a {coding platform} for homework submissions with {LLM} assistance.}
        \resumeItemListEnd

    \vspace{-2.0mm}

    \resumeSubheading
        {\text{1chooo.com}: A Monorepo of Personal Website and Blog} % Project Name
        {Jan. 2024 - present*} % Event Dates
        {Frontend Developer} % Role
        {\href{https://github.com/1chooo/1chooo.com}{\underline{\faGithub\ Code}} | \href{https://docs.1chooo.com}{\underline{{\faBook}\ Docs}} | \href{https://www.1chooo.com}{\underline{\faDesktop\ Demo}}} % Project Resources
        
        \vspace{-1.0mm}
        
        \resumeItemListStart
            \item {Refactored HTML/CSS template to {React} components, integrated with {Next.js Turborepo}, and tested with {Jest}.}
        \resumeItemListEnd

    \vspace{-2.0mm}
            
    \resumeSubheading
        {Lisp intepreter} % Project Name
        {Oct. 2023 - Jan. 2024} % Event Dates
        {Compiler Engineer} % Role
        {\href{https://github.com/1chooo/compiler-101/tree/main/mini-lisp-interpreter}{\underline{\faGithub\ Code}} | \href{https://github.com/1chooo/compiler-101/tree/main/mini-lisp-interpreter}{\underline{{\faBook}\ Docs}}} % Project Resources
        
        \vspace{-1.0mm}
        
        \resumeItemListStart
            \item {Crafted a {Lisp Interpreter} using {C} and {YACC} to parse and evaluate if expressions, variable definitions, numerical operations, nested functions, type checking, and recursion in Lisp.}
        \resumeItemListEnd
            
    \resumeSubHeadingListEnd

\vspace{-5.5mm}

%-----------AWARDS-----------------
\section{\textcolor{olive}{\textbf{Awards}}}

    \vspace{1.0mm}

    \begin{itemize}[
        leftmargin=0.20in, 
        label={-}, 
        itemsep=-2pt, 
        topsep=0pt,
        rightmargin=0.10in
    ]
        \item Top-Achieving Internship Team, eCloudValley Digital Technology \hfill \hspace{-0.2cm} {\footnotesize{Mar. 2024 - May. 2024}}
        \item Silver Internship Team, PEGATRON Corporation \hfill {\footnotesize{Jul. 2023 - Aug. 2023}}
        \item Second Place \& Sustainability Special Award, 2023 Weather Hackathon \hfill \textit{\footnotesize{May. 2023 - Aug. 2023}}
    \end{itemize}

\end{document}
